\section{Conference Talks}

\begin{bibenum}

    \item Pavlic, T.P., and S.C.~Pratt.
        Numerical Methods within the Ant Colony: The Illuminating Case
        of Multi-Objective Macronutrient Regulation in Eusocial Insects.
        In: \emph{2nd Workshop on Biological Distributed
        Algorithms~(BDA~2014)}, Austin, TX, October 11--12, 2014.
        Anticipated.

    \item Pavlic, T.P., and S.C.~Pratt. Understanding foraging patterns
        that achieve colony-level macronutrient regulation. In:
        \emph{2014 International Union for the Study of Social Insects
        International Congress~(IUSSI~2014)}, Queensland, Australia,
        July 13--18, 2014.

    \item Pavlic, T.P.
        Kinetic modeling of social insect behavior and beyond: Lessons
        from stochastic robotics. In: \emph{2013 International Symposium
        on Biomathematics and Ecology Education and
        Research~(BEER~2013)}, Arlington, VA, October 11--13, 2013.

    \item Pavlic, T.P., and S.C.~Pratt.
        Sequential\-/sampling models of quorum sensing in house-hunting
        \emph{Temnothorax} ants. In: \emph{50th Annual Conference of the
        Animal Behavior Society}, July~28--August~1, 2013.

    \item Pavlic, T.P. Speed\--accuracy tradeoffs in \emph{Temnothorax
        rugatulus} ants: Sequential\-/sampling models of quorum
        detection while house hunting. In: \emph{2013 Society for
        Mathematical Biology Annual Meeting and Conference~(SMB~2013)},
        June 10--13, 2013.

    \item Pavlic, T.P., and S.C.~Pratt. Sequential\-/sampling models of
        quorum detection in house-hunting ants. In: \emph{2012 North
        American Section Meeting of the International Union for the
        Study of Social Insects~(IUSSI-NAS~2012)}, October 5--7, 2012.

\end{bibenum}