\section{Conference Publications}

\begin{bibenum}

    \item Pavlic, T.P., A.~Adams, P.C.W.~Davies, and S.I.~Walker.
        Self-referencing cellular automata: A model of the evolution of
        information control in biological systems.
        In: \emph{Proceedings of the 14th International Conference on
        the Synthesis and Simulation of Living Systems~(ALIFE~14)},
        July 30~-- August 2, 2014.\\
        \doi{10.7551/978-0-262-32621-6-ch083}

    \item Pavlic, T.P.. Using Physical Stigmergy in Decentralized
        Optimization Under Multiple Non-separable Constraints: Formal
        Methods and an Intelligent Lighting Example. In:
        \emph{Proceedings of the 2014 Workshop on Nature Inspired
        Distributed Computing~(NIDISC~2014)}, May 19, 2014.

    \item Pavlic, T.P., S.~Wilson, G.P.~Kumar, and S.~Berman.
        An enzyme-inspired approach to stochastic allocation of robotic
        swarms around boundaries. In: \emph{Proceedings of the 16th
        International Symposium on Robotics Research~(ISRR~2013)},
        December 16--19, 2013.

    \item Kumar, G.P., A.~Buffin, T.P.~Pavlic, S.C.~Pratt, and
        S.M.~Berman. A Stochastic Hybrid System Model of Collective
        Transport in the Desert Ant \emph{Aphaenogaster cockerelli}. In:
        \emph{Proceedings of the 16th International Conference on Hybrid
        Systems: Communication and Control (HSCC~2013)}, April 8--11,
        2013. \doi{10.1145/2461328.2461349}

    \item Pavlic, T.P., and K.M.~Passino. Cooperative task-processing
        networks.\linebreak[4] In:~\emph{Proceedings of the Second
        International Workshop on Networks of Cooperating
        Objects (CONET~2011)}, April 11, 2011.

    \item Freuler, R.J., M.J.~Hoffmann, T.P.~Pavlic, J.M.~Beams,
        J.P.~Radigan, P.K.~Dutta, J.T.~Demel, and E.D.~Justen.
        Experiences with a Comprehensive Freshman Hands-On Course~--
        Designing, Building, and Testing Small Autonomous Robots. In:
        \emph{Proceedings of the 2003 American Society for Engineering
        Education Annual Conference \& Exposition}, 2003.

\end{bibenum}
