\section{Conference Posters}

\begin{bibenum}

    \item Pavlic, T.P. Physical Stigmergy for Decentralized Constrained
        Optimization: An Intelligent Lighting Example. In:
        \emph{Proceedings of the 4th International Conference on
        Cyber-Physical Systems~(ICCPS~2013)}, April 8--11, 2013.
        Poster abstract.

    \item Pavlic, T.P., S.~P.~Peddi, P.A.G.~Sivilotti, and B.W.~Weide.
        Getting Out of the Way~-- Safety Verification without
        Compromise. In: \emph{Proceedings of the 2012 IEEE/ACM Third
        International Conference on Cyber-Physical
        Systems~(ICCPS~2012)}, April 17--19, 2012. Poster abstract.

    \item Pavlic, T.P., P.A.G.~Sivilotti, A.D.~Weide, and B.W.~Weide.
        Verification of Smooth and Close Collision-Free Cruise Control.
        In: \emph{Proceedings of the 2011 Symposium on Control and
        Modeling Cyber-Physical Systems}, October 20--21, 2011. Poster
        abstract.

    \item {\"{O}}zg{\"{u}}ner, {\"{U}}., A.~Krishnamurthy,
        F.~{\"{O}}zg{\"{u}}ner, K.~Redmill, P.~Sivilotti, B.~Weide,
        and T.~Pavlic.
        CPS: Autonomous driving in urban environments.
        In: \emph{Proceedings of the 2011 NSF CPS PI Meeting},
        August 1--2, 2011. Poster abstract.

    \item Pavlic, T.P., and K.M.~Passino. Cooperative task
        processing. In: \emph{Proceedings of the ICAM 2009 Symposium:
        Emergence in Physical, Biological, and Social Systems IV},
        November 13, 2009. Poster abstract.

\end{bibenum}