\section{Grants}
\restartlist{bibenum}

\textbf{Awaiting Decision}

\begin{bibenum}
    \item Senior staff, ``A new multi-objective optimization framework
        for investigating mechanisms of social resource allocation'',
        NIH, NIGMS, 2014. Submitted.

\end{bibenum}

\blankline

\textbf{Recommended for Funding}

\begin{bibenum}

    \item Senior staff,
        ``CPS:Synergy: Collaborative Research: Collaborative Vehicular
        Systems'', NSF ECCS-1446730, \$914,802, January 1,~2015 to
        December 31,~2017. Recommended for funding.

\end{bibenum}

\blankline

\textbf{Awarded}

\begin{bibenum}

    \item Senior staff,
        ``Autonomous Driving in Mixed\-/Traffic Urban Environments'',
        NSF,\linebreak[4]
        \href{http://www.nsf.gov/awardsearch/showAward.do?AwardNumber=0931669}{ECCS-0931669},
        \$1,499,833, September 1,~2009 to August 31,~2012.

\end{bibenum}

\blankline

\textbf{Not Awarded}

\begin{bibenum}

    \item Senior staff, ``Informational architecture of collective
        decision making by \emph{Temnothorax} ants'', NSF, POLS, 2013.
        Not awarded.

    \item Senior staff,
        ``Biological stoichiometry of horizontal gene transfer and the
        social dynamics of microbial communities'', Army Research
        Office, 2013. Not awarded.

    \item Senior staff,
        ``Biologically-inspired strategies for collective transport and
        construction by multi-robot systems'', NSF, RI, 2013. Not
        awarded.

    \item Co\-/PI,
        ``An Ant Model System for the Study of Nutrient Balance in
        Social\-/Insect Pollinators'', USDA,
        NIFA\-/AFRI Foundational proposal, 2013. Not awarded.

    \item Senior staff,
        ``Cooperative LED Arrays for Preference\-/Adaptive Lighting in
        Smart Buildings'',
        NSF,
        EFRI\-/SEED preliminary proposal, 2009. Not awarded.

\end{bibenum}