\section{Invited Talks}

\begin{bibenum}

    \item Pavlic, T.P.
        The hidden demographics of distributed information processing:
        The role of intermediates in a social-insect colony. In:
        \emph{Social Insects as Models for Biological Complexity:
        Lessons Learned and Challenges on the Horizon}, symposium of the
        2014 Annual Meeting of the Entomological Society of
        America~(Entomology 2014). November 16--19, 2014. Anticipated.

    \item Pavlic, T.P. Understanding foraging patterns that achieve
        colony-level macronutrient regulation. In: \emph{ASU--UW\"{u}
        International Symposium and Workshop on Frontiers in Insect
        Behavior, Social Organization, and Evolution}, May 23--30, 2014.

    \item Pavlic, T.P. Take Home Messages: Evolution of Distributed
        Computational Networks. In: \emph{BEYOND Center Physics of
        Living Matter Workshop: Information, Complexity, and Life},
        February 24--25, 2013.

    \item Pavlic, T.P. Biomathematics at ``The New American
        University.'' In: ``Biomathematics Courses and Programs'' expert
        panel at 2013 International Symposium on Biomathematics and
        Ecology Education and Research~(BEER~2013),
        October 11--13, 2013.

    \item Pavlic, T.P. The Economic Framework: Constrained Optimization
        and Colony Collapse Disorder. In: \emph{Perspectives for
        Mathematical and Biological Interdisciplinary Research on
        Honeybees and Pollination}, June 14, 2013.

    \item Pavlic, T.P. Stochastic Robotics: Complexity,
        Compositionality, and Scalability. In: \emph{KI-Net Workshop on
        Kinetic Theory for the Emergence of Complex Behavior in Social
        and Economic Systems}, February 22--24, 2013.

\end{bibenum}