\section{Professional Experience}

\href{http://www.asu.edu/}{\textbf{Arizona State University}},
Tempe, AZ
\begin{outerlist}

    \item[] \textit{Associate Research Scientist}%
            \hfill \textbf{August 2014 to present}\\
        \textit{Postdoctoral Scholar}%
            \hfill \textbf{July 2012 to August 2014}
            \begin{innerlist}
                \item Supervisor:
                        \href{http://www.public.asu.edu/~spratt1/}%
                             {Professor Stephen C.~Pratt}

                \item Novel application of sophisticated quantitative
                    analysis and modeling techniques to animals, with
                    social insects as a particular focus.

                \item Development of new algorithms for robotics and
                    other autonomous systems based on animal behavior,
                    with focus on distributed decision making.

                \item Supervision of graduate and undergraduate students
                    in engineering, computer science, and biology in
                    tasks related to biological analysis and modeling as
                    well as technological bio\-/mimetic design.
            \end{innerlist}

\end{outerlist}

\halfblankline

\href{http://www.osu.edu/}{\textbf{The Ohio State University}},
Columbus, OH
\begin{outerlist}

    \item[] \textit{Postdoctoral Researcher}%
            \hfill \textbf{September 2010 to June 2012}
            \begin{innerlist}
                \item Funding:~\href{http://www.nfs.gov/}{National Science Foundation} Cyber\-/Physical Systems (ENG, \href{http://www.nsf.gov/div/index.jsp?div=eccs}{ECCS})
                \begin{innerlist}
                    \item[$-$] ``Autonomous Driving in Mixed\-/Traffic Urban Environments''
                        (grant~\href{http://www.nsf.gov/awardsearch/showAward.do?AwardNumber=0931669}{\#0931669})
                    \item[$-$] Supervisor (co\-/PI):
                        \href{http://www.cse.ohio-state.edu/~paolo/}%
                             {Professor Paolo A.~G.~Sivilotti}
                    \item[$-$] PI:
                        \href{http://www.ece.ohio-state.edu/~umit/}%
                             {Professor \"{U}mit \"{O}zg\"{u}ner}
                \end{innerlist}

                \item Development of new approaches to software
                    verification in the context of hybrid\-/state and
                    hybrid\-/time dynamical systems.

                \item Supervision of student design project for
                    novel vehicle\-/to\-/vehicle communications
                    systems to assist in adaptive cruise control.
            \end{innerlist}

\end{outerlist}

\halfblankline

\href{http://www.ni.com/}{\textbf{National Instruments}},
Austin, TX
\begin{outerlist}

\item[] \textit{Hardware R\&D Intern for Multifunction DAQ}%
        \hfill \textbf{June 2003 to September 2003}
\begin{innerlist}
\item Designed final verification test fixture for use with STC2 MIO
        products.
\item Designed and executed study of the effect of varying burn\-/in time
        on long\-/term drift of common industry voltage references.
\end{innerlist}

\item[] \textit{Hardware R\&D Intern for Multifunction DAQ}%
        \hfill \textbf{June 2002 to September 2002}
\begin{innerlist}
\item Designed and performed validation tests for 16-bit 800 kHz
        NI-6120 SMIO DAQ.

\item Designed high\-/quality source to use with NI-5411 arbitrary
        function generator.
\end{innerlist}

\end{outerlist}

\halfblankline

\textbf{\href{http://www.ibm.com/}{IBM} Network Storage},
Research Triangle Park, NC
\begin{outerlist}

\item[] \textit{Core Systems Software Developer for FlexNAS}%
        \hfill \textbf{June 2001 to September 2001}
\begin{innerlist}
\item Designed and implemented highly available multihop communications
        subsystem.
\item Participated in software development of various vital box
        services.
\end{innerlist}

\end{outerlist}

\halfblankline

\href{http://www.calltech.com/}{\textbf{CallTech Communications}},
Columbus, OH
\begin{outerlist}

\item[] \textit{Information Technology Systems Engineer}%
        \hfill \textbf{June 1997 to May 2001}
\begin{innerlist}
\item Responsible for the acquisition, setup, and administration of all
        hardware and software systems supporting
        \href{http://www.netwalk.com/}{NetWalk} Internet service and web
        presence provider.
\item Designed and implemented state\-/of\-/the\-/art open\-/source
        highly available load\-/balancing system supporting thousands of
        virtual servers.
\item Developed call\-/center software for clients such as
        CompuServe, AOL, and Priceline.
\end{innerlist}

\end{outerlist}

\halfblankline

\textbf{MegaLinx Communications}, Dublin, OH
\begin{outerlist}

\item[] \textit{Web Developer and Support Representative}%
        \hfill \textbf{June 1995 to May 1997}
\begin{innerlist}
\item Produced web content for commercial clients.
\item Assisted in administration of UltraSPARC, x86, 680x0, and PowerPC
        systems.
\item Developed multi\-/platform open\-/source file\-/sharing solution.
\item Provided technical support for Internet and web presence
        customers.
\end{innerlist}

\end{outerlist}
