\section{Student Advising}

\begin{bibsection}

    \item \textbf{Alyssa Adams}\\
        Graduate student in Physics, Arizona State University.
        Modeling and analysis of top\-/down causation in
        self\-/referencing cellular\-/automata models of the origins of
        life.
        Primary adviser: Sara I.~Walker.
        2013--2014.

    \item \textbf{Hana Putnam} and \textbf{Alex Nachman}\\
        Undergraduate students in Biology, Arizona State University.
        Laboratory support of research on decentralized nutrient
        regulation in \emph{Temnothorax rugatulus} ants.
        Primary adviser: Stephen C.~Pratt.
        2013.

    \item \textbf{Taylor Vance} and \textbf{P.~Logan Rogers}
        and \textbf{Betsy Siegworth}\\
        Undergraduate students in Biology, Arizona State University.
        Laboratory support of research on quorum detection by encounter
        rate in \emph{Temnothorax rugatulus} ants.
        Primary adviser: Stephen C.~Pratt.
        2013.

    \item \textbf{Sean T.~Wilson}\\
        Graduate student in Mechanical Engineering, Arizona State University.
        Dynamical modeling and analysis of the collective carrying
        behaviors of \emph{Aphaenogaster cockerelli} ants.
        Primary adviser: Spring Berman.
        2012--2013.

    \item \textbf{Ganesh P.~Kumar}\\
        Graduate student in Computer Science, Arizona State University.
        Bio\-/mimetic design of collective carrying algorithms for
        robotics, inspired by the ant \emph{Aphaenogaster cockerelli}.
        Primary adviser: Spring Berman.
        2012--2013.

    \item \textbf{Christal Johnson}\\
        Undergraduate student in Biology, Arizona State University.
        Modeling and analysis of quorum detection during emigration
        behavior in \emph{Temnothorax rugatulus} ants. Honors thesis.
        Primary adviser: Stephen C.~Pratt.
        2012.

    \item \textbf{Cory Henderson}, \textbf{James O'Donnell},
        \textbf{Ian Neack}, and \textbf{Patrick Whewell}\\
        Undergraduate students in Electrical and Computer Engineering,
        The Ohio State University.
        Group design project on retrofittable
        vehicle\-/to\-/vehicle communications system for
        adaptive\-/cruise\-/control in mixed\-/traffic environments.
        Primary adviser: Keith Redmill.
        2012.

    \item \textbf{Manas Agrawal}
        Graduate student in Computer Science and Engineering,
        The Ohio State University.
        Software verification and model checking applied to railroad
        safety problems.
        Primary adviser: Bruce W.~Weide.
        2012.

    \item \textbf{Sai Prathyusha Peddi}
        Graduate student in Computer Science and Engineering,
        The Ohio State University.
        Software verification applied to adaptive cruise
        control and instrumented intersection signal timing.
        Primary adviser: Bruce W.~Weide.
        2011--2012.

    \item \textbf{Jaeyong Park}.
        Graduate student in Electrical and Computer Engineering,
        The Ohio State University.
        Provably correct on\-/line control synthesis for
        autonomous vehicles with hybrid dynamics.
        Primary adviser: \"{U}mit \"{O}zg\"{u}ner.
        2011--2012.

\end{bibsection}