\section{Teaching Experience}

\href{http://www.asu.edu/}{\textbf{Arizona State University}},
Tempe, AZ
\begin{outerlist}

\item[] \textit{Guest Lecturer} for ANB~601: Research Strategies in Animal Behavior
    \hfill \textbf{October 2013}
    \begin{innerlist}
        \item Graduate-level course in animal behavior
        \item Lecture: ``Mathematical, Computational, and Experimental Modeling: Granularity and Parsimony''
    \end{innerlist}

\end{outerlist}

\halfblankline

\href{http://www.osu.edu/}{\textbf{The Ohio State University}},
Columbus, OH
\begin{outerlist}

\item[] \textit{Instructor}%
    \hfill \textbf{March~2012 to August~2012}
    \begin{innerlist}
        \item Instructor for ECE~683: Undergraduate Design Project
            %
            \begin{innerlist}
                \item Students designed retrofitable vehicle\-/to\-/vehicle
                    communications system to aid in the development of
                    verifiably safe adaptive cruise control.
                \item Design project folded into larger research project
                    on autonomous vehicles in mixed\-/traffic urban
                    environments.
            \end{innerlist}
    \end{innerlist}

\item[] \textit{Teaching Assistant}%
    \hfill \textbf{September 2007 to August 2009}\\
    (sample graded material and student evaluations available upon
    request)
    \begin{innerlist}
        \item Instructor for ECE~327: Electronic Devices and Circuits Laboratory I
        \begin{innerlist}
            \item Autumn~2007, Winter~(2) and Spring~2008~(2),
                Winter~(2) and Summer~2009

            % \item Sample student evaluations available upon request.

            \item Responsible for 1-hour lecture and supervision of
                3-hour laboratory. Students design and implement
                infrared modem and 8-ohm speaker driver.

            \item Authored hundreds of pages of course material
                archived at\\
                \url{http://www.tedpavlic.com/teaching/osu/ece327}.
        \end{innerlist}

        \halfblankline

        \item Grader for ECE~481 Ethics in Electrical and Computer Engineering
        \begin{innerlist}
            \item Autumn~2007 and Autumn~2008
        \end{innerlist}

        \halfblankline

        \item Instructor for ECE~209: Circuits and Electronics
            Laboratory
        \begin{innerlist}
            \item Autumn~2008

            % \item Sample student evaluations available upon request.

            \item Responsible for lecture and supervision of basic
                electronics laboratory.

            \item Authored material at
                \url{http://www.tedpavlic.com/teaching/osu/ece209}.
        \end{innerlist}

        \halfblankline

        \item Instructor for ECE~557: Control, Signals, and Systems
            Laboratory
        \begin{innerlist}
            \item Summer~2008~(2~sections) and Summer~2009

            % \item Sample student evaluations available upon request.

            \item Responsible for lecture and supervision of laboratory.
                Students used
                \href{http://www.mathworks.com/products/simulink/}{Simulink}
                and \href{http://www.dspaceinc.com/}{dSPACE} RTI1104
                units for linear system control design.

            \item Authored material at
                \url{http://www.tedpavlic.com/teaching/osu/ece557}.
        \end{innerlist}

        \halfblankline

        \item Lab Instructor for ECE~758: Control Systems Implementation
            Laboratory
        \begin{innerlist}
            \item Spring~2009~(2~sections)

            % \item Sample student evaluations available upon request

            \item Responsible for lecture and supervision of laboratory.
                Graduate and senior undergraduate students used
                \href{http://www.mathworks.com/products/simulink/}{Simulink},
                with \href{http://www.dspaceinc.com/}{dSPACE} RTI1104
                units for analysis of and advanced control implementation
                for linear and non\-/linear systems.

            \item Authored material at
                \url{http://www.tedpavlic.com/teaching/osu/ece758}.
        \end{innerlist}
    \end{innerlist}

\item[] \href{http://www.nsfgk12.org/}
        {\emph{National Science Foundation GK\-/12 Graduate Fellow}}
        \hfill \textbf{September 2006 to October 2007}
\begin{innerlist}
    \item[] Developed, implemented, and evaluated daily inquiry\-/based
        fourth\-/grade science lessons for a local inner\-/city public
        school class.
\end{innerlist}

\item[] \textit{Instructor}%
        \hfill \textbf{March 2002 to June 2004}
\begin{innerlist}
\item Member of \href{http://feh.eng.ohio-state.edu/}
                     {Fundamentals of Engineering for Honors}
      instructional team.
\item Special graduate teaching appointment as undergraduate.
\item Lectured weekly engineering laboratory for ENG~H191,
        H192, and~H193.
\item Trained in\-/class undergraduate teaching assistants in laboratory
        procedure.
\item Graded weekly lab reports and provided laboratory exams.
\end{innerlist}

\item[] \textit{Teaching Assistant}%
        \hfill \textbf{September 2000 to March 2002}
\begin{innerlist}
\item Assisted \href{http://feh.eng.ohio-state.edu/}
                    {Fundamentals of Engineering for Honors}
      instructional team.
\item Provided support to first\-/year engineering students (ENG~H191,
      H192, and H193).
\item Graded daily assignments on programming and drafting.
\item Developed on\-/line journal system for Physics Education Research
      Group~(PERG).
\end{innerlist}

\item[] \textit{Undergraduate Researcher}%
        \hfill \textbf{September 2000 to March 2002}
\begin{innerlist}
\item Participated in the
        \href{http://www.cse.ohio-state.edu/europa/}{Europa
        Undergraduate Research Forum}, a part of the
        \href{http://www.cse.ohio-state.edu/rsrg/}{Reusable Software
        Research Group}.
\item Studied component\-/based software engineering undergraduate
        pedagogy.
\item Researched changes to RESOLVE/C++ implementation for ANSI
        compliance.
\end{innerlist}

\item[] \textit{Grader}%
        \hfill \textbf{September 2001 to December 2001}
\begin{innerlist}
\item Graded daily electromagnetics assignments (ECE~311).
\end{innerlist}
\end{outerlist}